Testing the fidelity of simulations of black hole - galaxy co-evolution at $z\sim1.5$ with observations

### 2020-04-29 QSOII_paper/ApJ_manuscript/manuscript.tex
Tommaso's edits

In this study, we directly compare the mass ratios between SMBHs and their host galaxies of 32 type-1 (broad-line) AGNs from our recent observational study at $z\sim1.5$ \citep{Ding2020} to the predictions based on two independent state-of-the-art numerical simulations. \blue{The redshift range of our targets is chosen ($z<2$) when most of the SMBHs acquired their mass thus insensitive to initial conditions and growth mechanisms, which allows an identification of inaccurate or missing physics in the models. This redshift range is also low enough} to limit the effect of surface brightness dimming that would lower the success rate of detecting the underlying host galaxy with \hst. We describe the observed and simulated galaxies and their black holes in Section~\ref{sec:sample}. The comparisons between data and simulations are shown in Section~\ref{sec:result} and conclusion presented in Section~\ref{sec:conclusion}. Throughout this paper, we adopt a standard concordance
cosmology with $H_0 = 70$~\kmsMpc
, $\Omega_m = 0.30$,
and $\Omega_\Lambda = 0.70$. A Salpeter initial mass function is employed consistently to the
observed and simulated sample.

@@

To detect their host galaxies, we used \hst/WFC3 to obtain high-resolution (0\farcs0642 per pixel) infrared imaging data for 32 AGN systems (HST Program GO-15115). The filters F125W $(1.2<z<1.44)$ and F140W $(1.44<z<1.7)$ were employed, according to the redshift of each target. Six dithered exposures with a total exposure time $\sim2394s$ were co-added using the {\sc astrodrizzle} software package to generate a final image with a pixel scale as 0\farcs0642. We implemented the {\sc photuils} tools to remove contamination due to background light from both the sky and the detector. A full detailed description of the \hst\ data analysis can be found in \blue{the companion paper (D20)}.

@@

In the left panel of Figure~\ref{fig:MM_comp}, we compare the relation \mbh--\mstar~between observations and the \mbii\ simulation. It is clear that the simulated and observed samples are in good agreement. 
To quantify the agreement between the simulated and observed data, we use a linear regression to fit their relations. Our selection window has a hard cut on the \mbh\ value (i.e., vertical direction in Figure~\ref{fig:selectfunc}), and thus the scatter on the host properties are larger (horizontal direction). Thus, we fit the host properties (i.e., \mstar) as a function of \mbh. We adopt the {\sc Scipy} package to estimate the best-fit inference for the simulated sample. We then fit the observations based on the same slope value. The comparison results are shown in Figure~\ref{fig:MM_comp} (left panel), with the standard deviation of the residual indicated by the colored regions.
To estimate the {\it observed} scatter of the sample, we calculate the standard deviation of the fitted residual based on \mstar\ (i.e., along the $x$-axis). The histogram of the residual is presented in Figure~\ref{fig:offset_comp} (left panel). We find the standard deviation of the residual for observed and \mbii\ sample are similar, i.e., both equal to $\sim0.3$~dex. We manually change the slope value by its uncertainty level and find that the corresponding {\it observed} scatter barely changes ($<1\%$), meaning that the inferred scatter weakly depends on the fixed slope. \blue{To understand how much of the scatter is from the random noise, we measure the scatter \mbii\ without injecting any noise to the data. Adopting the same selecting window and using the linear regression approach, we estimate the scatter value as $\sim0.1$~dex. Note that this $\sim0.1$~dex scatter level is also controlled by our selection window, which shouldn't be considered as the intrinsic scatter of the overall sample.} We note that with different definitions to calculate the scatter, the inferred value may result in a more pronounced difference. In this particular work, we simply apply a common standard method (i.e., consideration of the measured residual in \mstar) to achieve a direct comparison between different samples. We perform the Kolmogorov-Smirnov (KS) test of the scatter distribution between observed and \mbii\ sample and infer the p-value as $\sim0.1$. Considering that the simulation sample has been processed to have the same uncertainty level and selection effect, we expect the \mbii\ sample and the observational sample have the same intrinsic scatter level. We adopt the python package {\sc Linmix}~\citep{Kelly2007} to estimate the {\it intrinsic} scatter based on the \mbii\ overall sample and obtain a level of $0.25$~dex.

@@

We also compare our data to predictions by the \sam. In contrast to N-body simulations which produce individual objects, the \sam\ uses an interaction-driven model~\citep{Menci2014} to calculate the number density of the galaxies. To make a direct comparison, we first randomly produce an overall sample based on the \sam\ predicted number density at $z=1.5$. Then, as in the \mbii\ analysis, we inject random scatter in the sample to account for uncertainties and apply the observational selection function. The resulting comparison of the  \mbh-\mstar\ relation is shown in Figure~\ref{fig:MM_comp} (right panel). We find that the best-fit result by the \sam\ model is well matched to the observation. However, the scatter of the \sam\ model is significantly larger ($\sim0.7$~dex) than observed (this is the total scatter accounting for the intrinsic scatter in the \sam\ distribution, observational uncertainties, and selection effects). \blue{Even without injecting random noise to \sam\ data, we find the scatter (considering selection effect) would up to $\sim0.6$~dex.}

@@

\blue{Implementing new physical assumptions to \sam\ is not straightforward to solve the tension as discovered in the scatter. 
%In practice, if one adjust the physical parameters in the SAM model, the scatter would not be as a tunable output. 
Increasing, for example, the efficiency of AGN feedback would change the colors of massive galaxies, while changing the Supernovae feedback efficiency would result in a different slope of the galaxy luminosity functions at the faint end. Most importantly, these changes would not appreciably affect the scatter, which originates from the assumption of interactions as triggers for BH accretion. In the \sam\ model, it is possible to switch to disk instabilities as triggers for accretion. However, this channel alone would not be able to yield the accretion rates necessary to power the most luminous quasars~\citep[see][]{Menci2014}. Implementing ``ad-hoc'', i.e., completely phenomenological and parametrized laws for the accretion, would require a long-lasting work on tuning the possible parameters exploring the impact of each choice not only on the observables connected to AGN, but also on the properties of the galaxy populations (e.g., colors, luminosity functions, etc.). In addition, such a new approach with massive efforts would possibly not provide deeper insights on the physical mechanisms driving the AGN-galaxy connection.}

@@

\blue{The redshifts of our 32 AGN systems cover the range $1.2<z<1.7$. It would be equally interesting to consider the evolution trend of the mass relation within this redshift range and make comparion with the simulation ones. Unfortunately, the limited sample size couldn't provide sufficient resolution at this board redshift range (see Figure~8 in D20). Thus, we only consider the sample with a single redshift bin at $z\sim1.5$ to compare with the simulations and the local measurements.}

>>>>

In this study, we directly compare the mass ratios between SMBHs and their host galaxies of 32 type-1 (broad-line) AGNs from our recent observational study at $z\sim1.5$ \citep{Ding2020} to the predictions based on two independent state-of-the-art numerical simulations. \blue{The redshift range of our targets is chosen ($z<2$) to coincide with the epoch when most of the SMBHs acquired their mass. This choice minimizes sensitivity to initial conditions and growth mechanisms, which in turn allows for an identification of inaccurate or missing physics in the models. This redshift range is also low enough} to limit the effect of surface brightness dimming that would lower the success rate of detecting the underlying host galaxy with \hst. We describe the observed and simulated galaxies and their black holes in Section~\ref{sec:sample}. The comparisons between data and simulations are shown in Section~\ref{sec:result} and conclusion presented in Section~\ref{sec:conclusion}. Throughout this paper, we adopt a standard concordance
cosmology with $H_0 = 70$~\kmsMpc
, $\Omega_m = 0.30$,
and $\Omega_\Lambda = 0.70$. A Salpeter initial mass function is employed consistently to the
observed and simulated sample.

@@

To detect their host galaxies, we used \hst/WFC3 to obtain high-resolution (0\farcs0642 per pixel) infrared imaging data for 32 AGN systems (HST Program GO-15115). The filters F125W $(1.2<z<1.44)$ and F140W $(1.44<z<1.7)$ were employed, according to the redshift of each target. Six dithered exposures with a total exposure time $\sim2394s$ were co-added using the {\sc astrodrizzle} software package to generate a final image with a pixel scale as 0\farcs0642. We implemented the {\sc photuils} tools to remove contamination due to background light from both the sky and the detector. A full detailed description of the \hst\ data analysis can be found in \blue{a companion paper (D20)}.

@@

In the left panel of Figure~\ref{fig:MM_comp}, we compare the relation \mbh--\mstar~between observations and the \mbii\ simulation. It is clear that the simulated and observed samples are in good agreement. 
To quantify the agreement between the simulated and observed data, we use a linear regression to fit their relations. Our selection window has a hard cut on the \mbh\ value (i.e., vertical direction in Figure~\ref{fig:selectfunc}), and thus the scatter on the host properties are larger (horizontal direction). Thus, we fit the host properties (i.e., \mstar) as a function of \mbh. We adopt the {\sc Scipy} package to estimate the best-fit inference for the simulated sample. We then fit the observations based on the same slope value. The comparison results are shown in Figure~\ref{fig:MM_comp} (left panel), with the standard deviation of the residual indicated by the colored regions.
To estimate the {\it observed} scatter of the sample, we calculate the standard deviation of the fitted residual based on \mstar\ (i.e., along the $x$-axis). The histogram of the residual is presented in Figure~\ref{fig:offset_comp} (left panel). We find the standard deviation of the residual for observed and \mbii\ sample are similar, i.e., both equal to $\sim0.3$~dex. We manually change the slope value by its uncertainty level and find that the corresponding {\it observed} scatter barely changes ($<1\%$), meaning that the inferred scatter weakly depends on the fixed slope. \blue{To understand how much of the scatter derives from random noise, we measure the scatter of \mbii\ without injecting any noise in the data. Adopting the same selecting window and using the linear regression approach, we estimate the scatter value as $\sim0.1$~dex. Note that this $\sim0.1$~dex scatter level is also controlled by our selection window, and thus it should not be considered as the intrinsic scatter of the overall sample.} In this particular work, we simply apply a common standard method (i.e., consideration of the measured residual in \mstar) to achieve a direct comparison between different samples. We perform the Kolmogorov-Smirnov (KS) test of the scatter distribution between observed and \mbii\ sample and infer the p-value as $\sim0.1$. Considering that the simulation sample has been processed to have the same uncertainty level and selection effect, we expect the \mbii\ sample and the observational sample have the same intrinsic scatter level. We adopt the python package {\sc Linmix}~\citep{Kelly2007} to estimate the {\it intrinsic} scatter based on the \mbii\ overall sample and obtain a level of $0.25$~dex.

@@

We also compare our data to predictions by the \sam. In contrast to N-body simulations which produce individual objects, the \sam\ uses an interaction-driven model~\citep{Menci2014} to calculate the number density of the galaxies. To make a direct comparison, we first randomly produce an overall sample based on the \sam\ predicted number density at $z=1.5$. Then, as in the \mbii\ analysis, we inject random scatter in the sample to account for uncertainties and apply the observational selection function. The resulting comparison of the  \mbh-\mstar\ relation is shown in Figure~\ref{fig:MM_comp} (right panel). We find that the best-fit result by the \sam\ model is well matched to the observation. However, the scatter of the \sam\ model is significantly larger ($\sim0.7$~dex) than observed (this is the total scatter accounting for the intrinsic scatter in the \sam\ distribution, observational uncertainties, and selection effects). \blue{Even without injecting random noise to \sam\ data, we find that the scatter (considering selection effects) would be $\sim0.6$~dex.}

@@

\blue{It is not straightforward to implementing new physical assumptions to \sam\  in order to solve the tension as discovered in the scatter. 
%In practice, if one adjust the physical parameters in the SAM model, the scatter would not be as a tunable output. 
Increasing, for example, the efficiency of AGN feedback would change the colors of massive galaxies, while changing the Supernovae feedback efficiency would result in a different slope of the galaxy luminosity functions at the faint end, which are constrained by other data. Most importantly, these changes would not appreciably affect the scatter, which originates from the assumption of interactions as triggers for BH accretion. In the \sam\ model, it is possible to switch to disk instabilities as triggers for accretion. However, this channel alone would not be able to yield the accretion rates necessary to power the most luminous quasars~\citep[see][]{Menci2014}. Implementing ``ad-hoc'', i.e., completely phenomenological and parametrized laws for the accretion, would require a long and detailed exploration of the possible parameters and the impact of each choice not only on the observables connected to AGN, but also on the properties of the galaxy populations (e.g., colors, luminosity functions, etc.). In addition, such a new approach with massive efforts would possibly not provide deeper insights on the physical mechanisms driving the AGN-galaxy connection.}

@@

\blue{Our sample of 32 AGN systems covers the range $1.2<z<1.7$. In principle it would be interesting to consider the evolution trend of the mass relation within the redshift range and make comparisons with the simulation as a function of cosmic time. Unfortunately, the limited sample size and precision of the measurement are not sufficient to resolve the evolution within this redshift range (see Figure~8 in D20). Thus, we only consider the sample with a single redshift bin at $z\sim1.5$ to compare with the simulations and the local measurements.}
